Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-21 paper/preprint/appendix.Rmd
add roc curve starts

Not done!

```{r}
#load(here("data/preprocessed_data/saycam_metadata.RData"))
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detectionsall_thresholds.RData"))
# where's ground truth? these columns just refer to detections, not gold sample human ratings..

#roc <- all_gold_sample_frames_op %>% group_by(detection_threshold) %>%
#  summarise(hand_pos = sum(hand_detected) / n(),
#            face_pos = sum(face_detected) / n()) 
# hmm shouldn't we have varying numbers of detection at different thresholds?

# can extract human ratings from hand_eval_ketan / face_eval_ketan:
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations

>>>>

```{r}
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations

evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

 return_tpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  tpr = tp / (tp + fn)
  return(tpr)
 }

return_fpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  fpr = fp / (fp + tn)
  return(fpr)
 }

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

```{r}
ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate')

ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate')
